An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps

### 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
fixed author info

---
documentclass: jss
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    address: >
      School of Mthematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{stephanie.kobakian@qut.edu.au}
    url: http://rstudio.com
title:
  plain: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps   
abstract: >
  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, statistics, cartogram]
preamble: >
  \usepackage{amsmath}
biblio-style: jss
output:
  rticles::jss_article:
    fig_caption: true
    citation_package: natbib
bibliography: sugarbag.bib
link-citations: true
---

@@

## Tasmania

>>>>

---
documentclass: jss
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    address: >
      School of Mathematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{stephanie.kobakian@qut.edu.au}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Melbourne, VIC, Australia
    email: \email{dicook@monash.edu}
title:
  plain: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps   
abstract: >
  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, statistics, cartogram]
preamble: >
  \usepackage{amsmath}
biblio-style: jss
output:
  rticles::jss_article:
    fig_caption: true
    citation_package: natbib
bibliography: sugarbag.bib
link-citations: true
---

@@

## Polygon set

### 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
fixed author info

\author{
Stephanie Kobakian\\Queensland University of Technology
}
\title{}

\Plainauthor{Stephanie Kobakian}
\Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
Application to Australian Maps}

@@

\Address{
    Stephanie Kobakian\\
  Queensland University of Technology\\
  School of Mthematical Sciences, Science and Engineering Faculty,
  Brisbane, QLD, Australia\\
  E-mail: \email{stephanie.kobakian@qut.edu.au}\\
  URL: \url{http://rstudio.com}\\~\\
  }

>>>>

\author{
Stephanie Kobakian\\Queensland University of Technology \And Dianne Cook\\Monash University
}
\title{}

\Plainauthor{Stephanie Kobakian, Dianne Cook}
\Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
Application to Australian Maps}

@@

\Address{
    Stephanie Kobakian\\
  Queensland University of Technology\\
  School of Mathematical Sciences, Science and Engineering Faculty,
  Brisbane, QLD, Australia\\
  E-mail: \email{stephanie.kobakian@qut.edu.au}\\

      Dianne Cook\\
  Monash University\\
  Department of Econometrics and Business Statistics, Melbourne, VIC,
  Australia\\
  E-mail: \email{dicook@monash.edu}\\
